Refunctionalization of Abstract Abstract Machines (Functional Pearl)

### 2018-05-30 paper/paper.tex
Update the style of subtitles in section related work

\textbf{Abstract Interpretation and Control-flow Analysis.}
\citeauthor{cousot1977abstract} invented abstract interpretation as a sound approach
to approximate a program's runtime behavior\cite{cousot1977abstract}.
Control flow analysis is one instance of abstract interpretation on functional programs
that can be traced to Jones \cite{jones1981flow}.
\citeauthor{Shivers:1988:CFA:53990.54007} introduces $k$-CFA which uses $k$ recent calling contexts as program contour that differentiates values from different contexts \cite{Shivers:1988:CFA:53990.54007, Shivers:1991:SSC:115865.115884}.
The modern formulation of control flow analysis is the abstracting abstract machines
methodology \cite{van2012systematic, van2010abstracting} which forms the starting point of this paper.
Modern programming languages such as Java\cite{might2010resolving} and Racket \cite{Tobin-Hochstadt:2012:HSE:2384616.2384655}
can also be modeled by the abstracting abstract machine approach.

\textbf{Defunctionalization and Refunctionalization.}
Defunctionalization and refunctionalization build connections between abstract
machines and interpreters.
\citeauthor{reynolds1972definitional} first shows defunctionalization as a program transformation technique that
can be used to transform higher-order functions to first-order functions
when specifying a programming language by an interpreter \cite{reynolds1972definitional}.
Refunctionalization is the reverse of this transformation.

@@

Fusion as one of the transformation in our paper is also studied by \citeauthor{Ohori:2007:LFF:1190216.1190241} \cite{Ohori:2007:LFF:1190216.1190241}.

\textbf{Pushdown Control Flow Analysis.}
In recent years, there are significant efforts~\cite{vardoulakis2010cfa2, earl2012introspective,
gilray2016pushdown, johnson2015abstracting} to achieve precise call/return
match based on small-step abstracting abstract machines.

@@

Our work establish the pushdown control-flow analysis through refunctionalization and a
proper caching algorithm. The call/return is naturally matched by the stack of 
the meta language.

\textbf{Abstracting Definitional Interpreters.}
Reynold's seminal paper \emph{Definitional interpreters for higher-order
  programming languages} \cite{reynolds1972definitional} shows that in
definitional interpreters, the defined language can inherit properties from the defining language.
With this insight, \citeauthor{darais2017abstracting} construct abstracting
definitional interpreters which automatically inherit the pushdown control-flow
property from its defining language because the defined language simply uses the stack of the
meta-language~\cite{darais2017abstracting}. \citeauthor{darais2017abstracting}'s abstracting
definitional interpreters work on direct-style programs, and is written in monadic style. One
of the advantages of monadic abstract interpreters is modular and composable, therefore
deploying different sensitivities or features is just applying a different monad.
Prior to that, \citeauthor{Sergey:2013:MAI:2491956.2491979} show a monadic
abstract interpreter for small-step semantics \cite{Sergey:2013:MAI:2491956.2491979}.

>>>>

\textit{Abstract Interpretation and Control-flow Analysis.}
\citeauthor{cousot1977abstract} invented abstract interpretation as a sound approach
to approximate a program's runtime behavior\cite{cousot1977abstract}.
Control flow analysis is one instance of abstract interpretation on functional programs
that can be traced to Jones \cite{jones1981flow}.
\citeauthor{Shivers:1988:CFA:53990.54007} introduces $k$-CFA which uses $k$ recent calling contexts as program contour that differentiates values from different contexts \cite{Shivers:1988:CFA:53990.54007, Shivers:1991:SSC:115865.115884}.
The modern formulation of control flow analysis is the abstracting abstract machines
methodology \cite{van2012systematic, van2010abstracting} which forms the starting point of this paper.
Modern programming languages such as Java\cite{might2010resolving} and Racket \cite{Tobin-Hochstadt:2012:HSE:2384616.2384655}
can also be modeled by the abstracting abstract machine approach. \\

\textit{Defunctionalization and Refunctionalization.}
Defunctionalization and refunctionalization build connections between abstract
machines and interpreters.
\citeauthor{reynolds1972definitional} first shows defunctionalization as a program transformation technique that
can be used to transform higher-order functions to first-order functions
when specifying a programming language by an interpreter \cite{reynolds1972definitional}.
Refunctionalization is the reverse of this transformation.

@@

Fusion as one of the transformation in our paper is also studied by 
\citeauthor{Ohori:2007:LFF:1190216.1190241} \cite{Ohori:2007:LFF:1190216.1190241}. \\

\textit{Pushdown Control Flow Analysis.}
In recent years, there are significant efforts~\cite{vardoulakis2010cfa2, earl2012introspective,
gilray2016pushdown, johnson2015abstracting} to achieve precise call/return
match based on small-step abstracting abstract machines.

@@

Our work establish the pushdown control-flow analysis through refunctionalization and a
proper caching algorithm. The call/return is naturally matched by the stack of 
the meta language. \\

\textit{Abstracting Definitional Interpreters.}
Reynold's seminal paper \emph{Definitional interpreters for higher-order
  programming languages} \cite{reynolds1972definitional} shows that in
definitional interpreters, the defined language can inherit properties from the defining language.
With this insight, \citeauthor{darais2017abstracting} construct abstracting
definitional interpreters which automatically inherit the pushdown control-flow
property from its defining language because the defined language simply uses the stack of the
meta-language~\cite{darais2017abstracting}. \citeauthor{darais2017abstracting}'s abstracting
definitional interpreters work on direct-style programs, and is written in monadic style. One
of the advantages of monadic abstract interpreters is modular and composable, therefore
deploying different sensitivities or features is just applying a different monad.
Prior to that, \citeauthor{Sergey:2013:MAI:2491956.2491979} show a monadic
abstract interpreter for small-step semantics \cite{Sergey:2013:MAI:2491956.2491979}.
